Scheeper's Meager-NWD Game and the Menger Game

### 2014-12-03 phd/dissertation/chapter5.tex
reproducing original proof of main ch 5 result

\begin{lem}
  If $\pl K\ktactwin{k+2}\gruKPGame{\pmb X}$, then
  $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$.
\end{lem}

\begin{proof}
  \newcommand{\hi}{\text{height}}
  \newcommand{\de}{\text{depth}}
  Fix an arbitrary $y\in X$. For $\pmb t\in \pmb X^{<\omega}$, define the
  following:
    \begin{itemize}
      \item $\hi(\pmb t)<\omega$ satisfying
            $|s|\leq \hi(\pmb t)$ for each
            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
      \item $\de(\pmb t)\in [X]^{<\omega}$ satisfying
            $x\in\de(\pmb t)$ for each
            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
      % \item $\pmb R(\pmb t)\in [\pmb X^{<\omega}]^{<\omega}$ such that
      %       $\pmb r\in \pmb R(\pmb t)$
      %       satisfies one of the following:
      %   \begin{itemize}
      %     \item $\pmb r(i)=c$ where $c\in C\cap\ran{\pmb t}$
      %     \item $\pmb r(i)=\<x,s\>$ where $s\leq\hi(\pmb t)$,
      %                                     $x\in\de(\pmb t)$
      %     \item $\pmb r(i)=\<y,s\>$ where $s\leq\hi(\pmb t)$
      %   \end{itemize}
    \end{itemize}

  For each compact set $C$, define $F(C)\in[\omega_1]^{<\omega}$ and
  $m(C)<\omega$ such that $C\subseteq K'_{F(C)}\cup L_{m(C)}$.

  Let $\sigma$ be a winning $k+2$-tactic for $\pl K$.
  For $\pmb t\in \pmb X^{<\omega}$, let $\pmb r\preceq \pmb t$ denote that
  $\pmb r$ is a subsequence of a permutation of $\pmb t$, and let
  $\pmb r\preceq_i \pmb t$ denote that $\pmb r$ is a subsequence of a
  permutation of $\pmb t\concat\<\<y,s\>\>$ for some $s\in 2^{\leq i}$.

  Let $M(\pmb t)=\max_{\pmb r\preceq \pmb t} m(\sigma(\pmb r\rest^{k+2}))$.
  We construct a $k+1$-tactic $\tau$ for $\pl K$ as follows:
    \[
      \tau(\pmb t)
        =
      \bigcup_{\pmb r\preceq_{|M(\pmb t)|} \pmb t}
      \sigma(\pmb r)
    \]
  Let $\pmb p:\omega\to\pmb X$ be a legal attack against $\tau$, so
    \[
      \pmb p(n)
        \not\in
      \bigcup_{m\leq n}
      \tau(\pmb p\rest^{k+1} m)
    \]
  Define the attack $\pmb q:\omega\to\pmb X$ as follows for $i<\omega$,
  $j<k+1$:
    \[
      \pmb q((k+2)i+j) = \pmb p((k+1)i+j)
    \]
    \[
      \pmb q((k+2)i+(k+1)) = \<y,a_{|M()|}\>
    \]

>>>>

\begin{lem}
  If $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$, then
  $\pl K\tactwin\gruKPGame{\pmb X}$.
\end{lem}

\begin{proof}
  Let $\sigma$ be a winning $(k+1)$-tactical strategy, and without loss of
  generality assume it ignores order.

  Define $S(x_0,\dots,x_{k},n)\in [C]^{<\omega}$ (increasing on $n$) and
  $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each
  $\<x_0,\dots,x_{k}\>\in X^{k+1}$,
  \[
    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}}
    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)
      \subseteq
    K'_{S(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
  \]
  and assume without loss of generality that
  \[
    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)
      =
    K'_{S(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))}
      \cup
    L_{m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))}
  \]

  Select an arbitrary point $y \in X$.
  Let $M^0(x,n)=m(x,y,\dots,y,n)$ and $M^{i+1}(x,n)=M^0(x,M^i(x,n)+1)$, and
  define the tactical strategy $\tau$ as follows:
  \[
    \tau(\<x,s\>)
      =
    K'_{S(x,y,\dots,y,M^k(x,|s|)+1)}
      \cup
    L_{M^k(x,|s|)+1}
  \]

  Let $\pmb p:\omega\to X\times 2^{<\omega}$ be a legal attack against
  $\tau$, such that $\pmb p(n)=\<x_n,s_n\>$.
  Then consider the attack $\pmb q:\omega\to X\times 2^{<\omega}$ against
  $\sigma$ defined by
    \[
      \pmb q((k+1)n)=\pmb p(n)=\<x_n,s_n\>
    \]
    \[
      \pmb q((k+1)n+(i+1))=\<y, a_{M^i(x_n,|s_n|)}\>
    \]
  for $i<k$.

  Since $\pmb p(n+1)\not\in\tau(\pmb p(n))$, it follows that
  $|s_{n+1}|\geq M^{i+1}(x_n,|s_n|)+1$; furthermore, for $i<k$,
    \[
      |s_n|
        <
      M^i(x_n,|s_n|)
        <
      M^i(x_n,|s_n|)+1
        \leq
      M^{i+1}(x_n,|s_n|)
        <
      M^{i+1}(x_n,|s_n|)+1
        \leq
      |s_{n+1}|
    \]
  so the second coordinate of $\pmb q(n)$ is always strictly increasing.

  By the definition of $\tau$,
  $\pmb q((k+1)n)=\pmb p(n)\not\in\sigma(\pmb q\rest^{k+1} (k+1)n)$.
  Since $\pmb q((k+1)n+(i+1))=\<y, a_{M^i(x_n,|s_n|)}\>\in X\times A$,
  $\pmb q((k+1)n+(i+1))\not\in K'_F$ for any $F\in[\omega_1]^{<\omega}$.

  Then it's sufficient to note that
    \[
      |a_{M^0(x_n,|s_n|)}|
        >
      M^0(x_n,|s_n|)
        =
      m(x_n,y,\dots,y,|s_n|)
    \]
  and
    \[
      |a_{M^{i+1}(x_n,|s_n|)}|
        >
      M^{i+1}(x_n,|s_n|)
        =
      m(x_n,y,\dots,y,M^i(x_n,|s_n|)+1)
    \]
  to show that
  $\pmb q((k+1)n+(i+1))\not\in\sigma(\pmb q\rest^{k+1} (k+1)n+(i+1))$.

% Note that $m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))$ is increasing throughout this play of the game versus $\sigma$:
%   \[
%     m(x_i,x',\dots,x',\max(|s_i|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
%   \]
%   \[
%     =
%     m(x_i,x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
%   \]
%   \[
%     =
%     m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
%   \]
%   \[
%     \leq
%     |s_{i+1}|
%   \]
%   \[
%     <
%     M^0(x_{i+1},|s_{i+1}|)
%   \]
%   \[
%     =
%     m(x_{i+1},x',\dots,x',|s_{i+1}|)
%   \]
%   \[
%     =
%     m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
%   \]
%   \[
%     =
%     |{z_{m(x_{i+1},x',\dots,x',|s_{i+1}|)}}|
%   \]
%   \[
%     =
%     |{z_{M^0(x_{i+1},|s_{i+1}|)}}|
%   \]
%   \[
%     <
%     |{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
%   \]
%   \[
%     <
%     m(x_{i+1},x',\dots,x',|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
%   \]
%   \[
%     =
%     m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^1(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i},|s_{i}|)}}^\frown\<1\>|))
%   \]
%   \[
%     \vdots
%   \]
%   \[
%     <
%     m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|))
%   \]

% We turn to showing that $\<x', {z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move. Since ${z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
%   \[
%     L_{m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{i},|s_{i}|)}}^\frown\<1\>|))}
%   \]
%   \[
%     =
%     L_{m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)}
%   \]
% which we can see here:
%   \[
%     m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
%   \]
%   \[
%     =
%     m(x_{i+1},x',\dots,x',M^{j-1}(x_{i+1},|s_{i+1}|)+1)
%   \]
%   \[
%     =
%     M^0(x_{i+1},M^{j-1}(x_{i+1},|s_{i+1}|)+1)
%   \]
%   \[
%     =
%     M^j(x_{i+1},s_{i+1})
%   \]
%   \[
%     <
%     |{z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
%   \]

% We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids
%   \[
%   L_{m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))}
%   \]
% since
%   \[
%     m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
%   \]
%   \[
%     =
%     m(x_{i},x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
%   \]
%   \[
%     =
%     m(x_{i},x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
%   \]
%   \[
%     \leq
%     |s_{i+1}|
%   \]

% Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, for $h\leq i$ it avoided
%   \[
%     K^*_{S(x_h,x',\dots,x',M^{k-1}(x_h,|s_h|)+1)}
%   \]
%   \[
%     =
%     K^*_{S(x_h,x',\dots,x',\max(|s_h|,|{z_{M^{0}(x_h,|s_h|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_h,|s_h|)}}^\frown\<1\>|))}
%   \]
% and when $h<i$, we see it avoids both:
%   \[
%     K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))}
%   \]
%   \[
%     =
%     K^*_{S(x_{h+1},x',\dots,x',|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|)}
%   \]
%   \[
%     =
%     K^*_{S(x_{h+1},x',\dots,x',M^{j-1}(x_{h+1},|s_{h+1}|)+1)}
%   \]
%   \[
%     \subseteq
%     K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
%   \]
% and:
%   \[
%     K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))}
%   \]
%   \[
%     =
%     K^*_{S(x_{h+1},x',\dots,x',|s_{k+1}|)}
%   \]
%   \[
%     \subseteq
%     K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
%   \]
